---
title: "stimuli-participant similarity"
output: html_document
date: "2023-05-31"
---


```{r}
nonlinearity_dfsel

table(nonlinearity_dfsel$Dataset, nonlinearity_dfsel$morph)

colnames(nonlinearity_dfsel)
library(reshape2)

# Apply dcast for each numeric variable
nonlinearity_df = dcast(nonlinearity_dfsel,  face_id + face_unique + Dataset + Emotion ~ morph, value.var = "nonlinearity")
linearity_df = dcast(nonlinearity_dfsel, face_id + face_unique + Dataset + Emotion ~ morph, value.var = "linearity")
curvature_df = dcast(nonlinearity_dfsel, face_id + face_unique + Dataset + Emotion ~ morph, value.var = "curvature")

# Merge the data frames together by all non-numeric variables
nonlinearity_df_dcast = Reduce(function(x, y) merge(x, y), list(nonlinearity_df, linearity_df, curvature_df))
nonlinearity_df_dcast
# more efficient
# Pivot data to wider format
require(tidyverse)
nonlinearity_dfsel_wide <- nonlinearity_dfsel %>%
  pivot_wider(names_from = morph, 
              values_from = c(nonlinearity, linearity, curvature), 
              names_sep = "_")


# Reshape data
require(data.table)
nonlinearity_df_dcast <- dcast(setDT(nonlinearity_dfsel), face_unique + Dataset + Emotion ~ morph, 
                 value.var = c("nonlinearity", "linearity",
                               "curvature","entropy"), 
                 fun.aggregate = mean, na.rm = TRUE)

nonlinearity_df_dcast
table(nonlinearity_df_dcast$face_unique)

table(nonlinearity_df_dcast$Dataset)

nonlinearity_df_dcast%>%
  ggplot(aes(linearity_Original, linearity_Morph))+
  geom_point()+
  geom_smooth(method = "lm", se = F)+
  facet_grid(~Dataset)

nonlinearity_df_dcast%>%
  ggplot(aes(curvature_Original, curvature_Morph, colour = Emotion, 
             shape = Emotion))+
  geom_point()+
  # geom_smooth(method = "lm", se = F)+
  facet_grid(~Dataset)+
  geom_vline(xintercept = 0)+
  geom_hline(yintercept = 0)

# One thought here is that the incorporated stimuli (i.e., where one #metricis high morph and low for the other) should produce the largest #perceptual rating difference. 
# We can do this by defining the quadrants and computing the differences, #or by calculating the difference between the morph and the original, then #computing the average difference for participants' ratings.
  
head(nonlinearity_df_dcast)

nonlinearity_df_dcast

# This code computes the differences between 'Original' and 'Morph' for each of the numeric variables (nonlinearity, linearity, curvature, entropy) and adds these as new columns to the dataframe.

nonlinearity_df_dcast<- nonlinearity_df_dcast %>%
  mutate(
    diff_Nonlin_Orig_Morph = nonlinearity_Original - nonlinearity_Morph,
    diff_Lin_Orig_Morph = linearity_Original - linearity_Morph,
    diff_Curv_Orig_Morph = curvature_Original - curvature_Morph,
   diff_Entropy_Orig_Morph = entropy_Original - entropy_Morph
  )


# select just essetial columns
colnames(is.na(db_ASC_NT_2023))

table(is.na(db_ASC_NT_2023$linearity))
db_ASC_NT_2021


db_ASC_NT_2023_NT<-db_ASC_NT_2021%>%subset(db_ASC_NT_2021$Group == "NT")

colnames(db_ASC_NT_2023_NT)
db_ASC_NT_2023_NT
db_ASC_NT_2023_NT$Actor_ID
db_ASC_NT_2023_NT$matched

db_ASC_NT_2023_NT<-   db_ASC_NT_2023_NT%>%select(c(1:4,83,84,86,88,24,6:8,10,15))
colnames(db_ASC_NT_2023_NT)
# db_ASC_NT_2023$Recognacc
# 
# table(is.na(nonlinearity_dfsel$linearity))
# 
# unique(db_ASC_NT_2023_NT$Emotion)
# unique(nonlinearity_dfsel$Emotion)
# unique(nonlinearity_dfsel$stim_id)
# unique(db_ASC_NT_2023_NT$stim_id)


```

debugging
# Define two vectors
vector1 <- unique(nonlinearity_dfsel$stim_id)
vector2 <- unique(db_ASC_NT_2023_NT$stim_id)

# need to replacejoy for happiness, note that this emans the lmer models need to be re-analysed

# Replace 'cats' with 'dogs'
nonlinearity_dfsel$stim_id<- gsub("Joy", "Happiness", nonlinearity_dfsel$stim_id)


# Find the differences
diff_vector1_vector2 <- setdiff(vector1, vector2)  # Elements in vector1 but not in vector2
diff_vector2_vector1 <- setdiff(vector2, vector1)  # Elements in vector2 but not in vector1

print(paste("Elements in vector1 but not in vector2: ", paste(diff_vector1_vector2, collapse=", ")))
print(paste("Elements in vector2 but not in vector1: ", paste(diff_vector2_vector1, collapse=", ")))


```{r}

# db_ASC_NT_2023_NT<- left_join(db_ASC_NT_2023_NT, nonlinearity_dfsel)
# table(is.na(db_ASC_NT_2023_NT$linearity)) #should be all FALSE
# db_ASC_NT_2023_NT<-db_ASC_NT_2023%>%subset(db_ASC_NT_2023$Group == "NT")%>%
#   select(c(1:4,24,6:8,10,15,104,106,107,110:113))

colnames(db_ASC_NT_2023_NT)

# Reshape data


db_ASC_NT_2023_NT
  
table(is.na(db_ASC_NT_2023_NT$linearity))

table(is.na(db_ASC_NT_2023_NT$linearity))
  
colnames(db_ASC_NT_2023_NT)
db_ASC_NT_2023_NT$Block<-NULL
db_ASC_NT_2023_NT$face_unique<- substr(db_ASC_NT_2023_NT$stim_id,1,3)

db_ASC_NT_2023_NT
colnames(db_ASC_NT_2023_NT)

db_ASC_NT_2023_NT$Emotion
matched
db_ASC_NT_2023_NT<-db_ASC_NT_2023_NT%>%
  ungroup()

colnames(db_ASC_NT_2023_NT)
colnames(db_ASC_NT_2023_NT[,c(1,3,5,7,8,13,9:12)])


DT_wide <- melt(db_ASC_NT_2023_NT[,c(1,3,4,5,7,8,13,9:14,15)], 
                id.vars = c("ParticipantPrivateID", "Emotion", "DATASET","face_unique", "VideoType","matched"),
                measure.vars = c("AnswerRating_Intensity", "AnswerRating_Naturality", 
                                 "Recognacc", "AnswerRating_Valence"),
                variable.name = "Metric", value.name = "Value")

unique(DT_wide$Value)
table(is.na(DT_wide$Value))

DT_wide2 <- dcast(DT_wide, ParticipantPrivateID + Emotion + DATASET + face_unique+matched ~ paste0(Metric, "_", VideoType),
                 value.var = "Value",
                 fun.aggregate = mean,
                 na.rm = TRUE)

colnames(DT_wide2)


table(is.na(DT_wide2$AnswerRating_Intensity_Morph))

# Replace NaN with NA in a dataframe
df <- data.frame(a = c(1, 2, NaN, 4, 5), 
                 b = c(NaN, 2, 3, 4, 5))

DT_wide2_matched<- DT_wide2%>%subset(matched == "YES")

DT_wide2[] <- lapply(DT_wide2, function(x) {x[is.nan(x)] <- NA; x})
DT_wide2_matched
DT_wide2_matched[] <- lapply(DT_wide2_matched, function(x) {x[is.nan(x)] <- NA; x})
DT_wide2_matched
```


```{r}
# Add new columns computing the differences
options(scipen = 999)

# lest try remove NA rows

DT_wide2naomit<- na.omit(DT_wide2)
DT_wide2_matchednaomit<- na.omit(DT_wide2_matched)
DT_wide2_matchednaomit
```
```{r}
table(DT_wide2_matchednaomit$ParticipantPrivateID)
unique(DT_wide2naomit$ParticipantPrivateID)

DT_wide2naomit$ParticipantPrivateID<- as.factor(as.character(DT_wide2naomit$ParticipantPrivateID))
DT_wide2naomit$ParticipantPrivateID

#DT_wide2_matchednaomit
DT_wide2_matchednaomit$ParticipantPrivateID<- as.factor(as.character(DT_wide2_matchednaomit$ParticipantPrivateID))
DT_wide2_matchednaomit$ParticipantPrivateID

table(DT_wide2_matchednaomit$ParticipantPrivateID, DT_wide2_matchednaomit$DATASET)



# DT_wide2naomi
# DT_wide2test<- DT_wide2%>%
#   group_by(ParticipantPrivateID, Emotion, DATASET, face_unique)%>%
#   summarise_if(is.numeric, mean, na.rm = T)
# 
# cor(abs(DT_wide2test$AnswerRating_Intensity_Morph-
# DT_wide2test$AnswerRating_Intensity_Original),abs(DT_wide2test$AnswerRating_Valence_Morph-
# DT_wide2test$AnswerRating_Valence_Original))


cor(DT_wide2test$AnswerRating_Intensity_Morph,DT_wide2test$AnswerRating_Intensity_Original)
DT_wide2naomit<-DT_wide2naomit%>%
  mutate(
    diff_Intensity = AnswerRating_Intensity_Original - AnswerRating_Intensity_Morph,
    diff_Naturality = AnswerRating_Naturality_Original - AnswerRating_Naturality_Morph,
    diff_Recognition = Recognacc_Original - Recognacc_Morph,
    diff_Valence = AnswerRating_Valence_Original - AnswerRating_Valence_Morph  )
    # diff_Curvature = curvature_Original - curvature_Morph,
    # diff_Entropy = entropy_Original - entropy_Morph,
    # diff_Linearity = linearity_Original - linearity_Morph,
    # diff_Nonlinearity = nonlinearity_Original - nonlinearity_Morph

    
    DT_wide2naomit%>%
  ggplot(aes(abs(diff_Naturality),abs(diff_Valence)))+
  # geom_jitter()+
  geom_point()+
  # geom_smooth(method = "lm",se = F)+
  facet_grid(~DATASET)


    
    nonlinearity_df_dcast$linearity_quadrant<- 
  left_join(nonlinearity_df_dcast,  DT_wide2naomit)%>%
         group_by(face_unique,DATASET, Emotion )%>%
    summarise_if(is.numeric, mean, na.rmn = T)%>%
    ggplot(aes(abs(diff_Curv_Orig_Morph), abs(diff_Valence)))+
    geom_point()+
    geom_smooth(method = 'lm', se = F)+
    # facet_grid(~DATASET)+
    ggpubr::stat_cor()
  
    left_join(nonlinearity_df_dcast,  DT_wide2naomit)%>%
         group_by(face_unique,DATASET, Emotion )%>%
    summarise_if(is.numeric, mean, na.rmn = T)%>%
    ggplot(aes((diff_Curv_Orig_Morph), (diff_Valence)))+
    geom_point()+
    geom_smooth(method = 'lm', se = F)+
    # facet_grid(~DATASET)+
    ggpubr::stat_cor()
    
    
        left_join(nonlinearity_df_dcast,  DT_wide2naomit)%>%
         group_by(face_unique,DATASET, Emotion )%>%
    summarise_if(is.numeric, mean, na.rmn = T)%>%
    ggplot(aes(abs(diff_Lin_Orig_Morph), abs(diff_Valence)))+
    geom_point()+
    geom_smooth(method = 'lm', se = F)+
    # facet_grid(~DATASET)+
    ggpubr::stat_cor()
        
        
        nonlinearity_df_dcast$linearity_quad <-if_else(nonlinearity_df_dcast$linearity_Morph>0 &
                                                         nonlinearity_df_dcast$linearity_Original
                                                       >0, 1, 
                                                       
                                                       
                                                       if_else(nonlinearity_df_dcast$linearity_Morph>0 &
                                                         nonlinearity_df_dcast$linearity_Original
                                                       <0, 2, 
                                                       
                                                         if_else(nonlinearity_df_dcast$linearity_Morph<0 &
                                                         nonlinearity_df_dcast$linearity_Original
                                                       <0, 1,
                                                        if_else(nonlinearity_df_dcast$linearity_Morph<0 &
                                                         nonlinearity_df_dcast$linearity_Original
                                                       >0, 2,0)))
                                                       
                                                       )
        
        
        
nonlinearity_df_dcast$curv_quad <-if_else(nonlinearity_df_dcast$curvature_Morph>0 &
                                                         nonlinearity_df_dcast$curvature_Original
                                                       >0, 1, 
                                                       
                                                       
                                                       if_else(nonlinearity_df_dcast$curvature_Morph>0 &
                                                         nonlinearity_df_dcast$curvature_Original
                                                       <0, 2, 
                                                       
                                                         if_else(nonlinearity_df_dcast$curvature_Morph<0 &
                                                         nonlinearity_df_dcast$curvature_Original
                                                       <0, 1,
                                                        if_else(nonlinearity_df_dcast$curvature_Morph<0 &
                                                         nonlinearity_df_dcast$curvature_Original
                                                       >0, 2,0)))
                                                       
                                                       )
    
  nonlinearity_df_dcast%>%
    ggplot(aes(linearity_Morph, linearity_Original, shape = Emotion, color = Emotion))+
             geom_point()+
    # facet_grid(~Dataset)+
    geom_vline(xintercept = 0)+
    geom_hline(yintercept = 0)
  
  
    nonlinearity_df_dcast%>%
    ggplot(aes(curvature_Morph, curvature_Original, shape = Emotion, color = Emotion))+
             geom_point()+
    # facet_grid(~Dataset)+
    geom_vline(xintercept = 0)+
    geom_hline(yintercept = 0)
```

```{r}
   left_join(nonlinearity_df_dcast,  DT_wide2naomit)%>%
         # group_by(face_unique,Dataset, Emotion )%>%
         group_by(ParticipantPrivateID,linearity_quad,Dataset )%>%
    summarise_if(is.numeric, mean, na.rmn = T)%>%
    ggplot(aes(linearity_quad, abs(diff_Valence)))+
  stat_summary(geom="pointrange")+
    # geom_jitter()
      facet_grid(~Dataset)


   left_join(nonlinearity_df_dcast,  DT_wide2naomit)%>%
          group_by(ParticipantPrivateID,curv_quad,Dataset )%>%
    summarise_if(is.numeric, mean, na.rmn = T)%>%
    ggplot(aes(as.factor(curv_quad), abs(diff_Valence)))+
  stat_summary(geom="pointrange")+
      # geom_jitter(width = .1)+
     geom_smooth(aes(group = ParticipantPrivateID), method = 'lm', se = F)+
    # geom_point()+
      facet_grid(~Dataset)
   
```
   
   
   #diff_Intensity 
    left_join(nonlinearity_df_dcast,  DT_wide2naomit)%>%
         # group_by(face_unique,Dataset, Emotion )%>%
         group_by(ParticipantPrivateID,linearity_quad,Dataset )%>%
    summarise_if(is.numeric, mean, na.rmn = T)%>%
    ggplot(aes(linearity_quad, abs(diff_Intensity)))+
  stat_summary(geom="pointrange")+
    # geom_jitter()
      facet_grid(~Dataset)


   left_join(nonlinearity_df_dcast,  DT_wide2naomit)%>%
          group_by(ParticipantPrivateID,curv_quad,Dataset )%>%
    summarise_if(is.numeric, mean, na.rmn = T)%>%
    ggplot(aes(as.factor(curv_quad), abs(diff_Intensity)))+
  stat_summary(geom="pointrange")+
      # geom_jitter(width = .1)
    # geom_point()+
      facet_grid(~Dataset)
   
   # naturality
   
  #diff_Naturality 
    left_join(nonlinearity_df_dcast,  DT_wide2naomit)%>%
         # group_by(face_unique,Dataset, Emotion )%>%
         group_by(ParticipantPrivateID,linearity_quad,Dataset )%>%
    summarise_if(is.numeric, mean, na.rmn = T)%>%
    ggplot(aes(linearity_quad, abs(diff_Naturality)))+
  stat_summary(geom="pointrange")+
    # geom_jitter()
      facet_grid(~Dataset)


   left_join(nonlinearity_df_dcast,  DT_wide2naomit)%>%
          group_by(ParticipantPrivateID,curv_quad,Dataset )%>%
    summarise_if(is.numeric, mean, na.rmn = T)%>%
    ggplot(aes(as.factor(curv_quad), abs(diff_Naturality)))+
  stat_summary(geom="pointrange")+
      # geom_jitter(width = .1)
    # geom_point()+
      facet_grid(~Dataset)  
   
   # accuracy
   
   left_join(nonlinearity_df_dcast,  DT_wide2naomit)%>%
          group_by(ParticipantPrivateID,curv_quad,Dataset )%>%
    summarise_if(is.numeric, mean, na.rmn = T)%>%
    ggplot(aes(as.factor(curv_quad), abs(diff_Intensity)))+
  stat_summary(geom="pointrange")+
      # geom_jitter(width = .1)
    # geom_point()+
      facet_grid(~Dataset)
   
   # naturality
   
  #diff_Recognition 
    left_join(nonlinearity_df_dcast,  DT_wide2naomit)%>%
         # group_by(face_unique,Dataset, Emotion )%>%
         group_by(ParticipantPrivateID,linearity_quad,Dataset )%>%
    summarise_if(is.numeric, mean, na.rmn = T)%>%
    ggplot(aes(linearity_quad, abs(diff_Recognition)))+
  stat_summary(geom="pointrange")+
    # geom_jitter()
      facet_grid(~Dataset)


   left_join(nonlinearity_df_dcast,  DT_wide2naomit)%>%
          group_by(ParticipantPrivateID,curv_quad,Dataset,Emotion )%>%
    summarise_if(is.numeric, mean, na.rmn = T)%>%
    ggplot(aes(as.factor(curv_quad), abs(diff_Recognition)))+
  stat_summary(geom="pointrange")+
      # geom_jitter(width = .1)
    # geom_point()+
      facet_grid(Emotion~Dataset)  
   
   
diff_dataset<-   left_join(nonlinearity_df_dcast,  DT_wide2naomit)
diff_dataset$stim_idnew <-paste0(diff_dataset$face_unique,diff_dataset$Emotion,paste0(diff_dataset$Dataset))
diff_dataset$stim_idnew
diff_dataset<- diff_dataset%>%
mutate(diff_Curv_Orig_Morph_abs= abs(diff_Curv_Orig_Morph),
       diff_Lin_Orig_Morph_abs = abs(diff_Lin_Orig_Morph),
       diff_Valence_abs = abs(diff_Valence))

mod_diff<- list()       
 mod_diff$val_diff<- lmer(diff_Valence_abs ~Dataset*(diff_Lin_Orig_Morph_abs+diff_Curv_Orig_Morph_abs)+
       (1|ParticipantPrivateID)+(1|stim_idnew),
     REML = FALSE,
     data = diff_dataset)
 
 diff_dataset$curv_quad<- as.factor(diff_dataset$curv_quad)
 diff_dataset$linearity_quad<- as.factor(diff_dataset$linearity_quad) 
 
 
```{r}
  
 mod_diff$val_diff<- lmer(diff_ ~Dataset*(linearity_quad+curv_quad)+
       (1|ParticipantPrivateID)+
         (1|stim_idnew),
     REML = FALSE,
     data = diff_dataset)
 
 
 anova( mod_diff$val_diff)

```

   left_join(nonlinearity_df_dcast,  DT_wide2naomit)%>%
         group_by(face_unique,DATASET, Emotion )%>%
    summarise_if(is.numeric, mean, na.rmn = T)%>%
    ggplot(aes(abs(diff_Lin_Orig_Morph), abs(diff_Valence)))+
    geom_point()+
    geom_smooth(method = 'lm', se = F)+
    # facet_grid(~DATASET)+
    ggpubr::stat_cor()



    
    
     left_join(nonlinearity_df_dcast,  DT_wide2naomit)%>%
         group_by(face_unique,DATASET, Emotion )%>%
    summarise_if(is.numeric, mean, na.rmn = T)%>%
    ggplot(aes(abs(diff_Curv_Orig_Morph), abs(diff_Valence)))+
    geom_point()+
    geom_smooth(method = 'lm', se = F)+
    # facet_grid(~DATASET)+
    ggpubr::stat_cor()
      
      
```
  
  
  
    left_join(nonlinearity_df_dcast,  DT_wide2test)%>%
    ggplot(aes(abs(diff_Lin_Orig_Morph), abs(diff_Intensity)))+
    geom_point()+
    geom_smooth(method = 'lm', se = F)+
    facet_grid(~Dataset)+
    ggpubr::stat_cor()
    
      left_join(nonlinearity_df_dcast,  DT_wide2test)%>%
    ggplot(aes(abs(diff_Curv_Orig_Morph), abs(diff_Intensity)))+
    geom_point()+
    geom_smooth(method = 'lm', se = F)+
    facet_grid(~Dataset)+
    ggpubr::stat_cor()
  
      
          left_join(nonlinearity_df_dcast,  DT_wide2test)%>%
    ggplot(aes(abs(diff_Lin_Orig_Morph), abs(diff_Recognition)))+
    geom_point()+
    geom_smooth(method = 'lm', se = F)+
    facet_grid(~Dataset)+
    ggpubr::stat_cor()
    
      left_join(nonlinearity_df_dcast,  DT_wide2test)%>%
        group_by(face_unique,DATASET, Emotion )%>%
    ggplot(aes(abs(diff_Curv_Orig_Morph), abs(diff_Recognition)))+
    geom_point()+
    geom_smooth(method = 'lm', se = F)+
    facet_grid(~Dataset)+
    ggpubr::stat_cor()
      
```
  
  
  DT_wide2%>%
  mutate(
    diff_Intensity = AnswerRating_Intensity_Original - AnswerRating_Intensity_Morph,
    diff_Naturality = AnswerRating_Naturality_Original - AnswerRating_Naturality_Morph,
    diff_Recognition = AnswerRating_Recognition_Original - AnswerRating_Recognition_Morph,
    diff_Valence = AnswerRating_Valence_Original - AnswerRating_Valence_Morph,
    diff_Curvature = curvature_Original - curvature_Morph,
    diff_Entropy = entropy_Original - entropy_Morph,
    diff_Linearity = linearity_Original - linearity_Morph,
    diff_Nonlinearity = nonlinearity_Original - nonlinearity_Morph
  )
  group_by(Emotion, DATASET, face_unique)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(abs(diff_Linearity)))+
  geom_histogram()
  geom_point()+
  # geom_smooth(method = "lm",se = F)+
  facet_grid(~DATASET)+
  xlim(0,.1)
  ggpubr::stat_cor()
  
nonlinearity_dfsel%>%
  ggplot(aes(linearity))+
  geom_histogram()

db_ASC_NT_2023_NT%>%
  group_by(filename,VideoType,DATASET)%>%
  summarise_if(is.numeric, mean, na.rm = T)%>%
    ggplot(aes(linearity))+
  geom_histogram()+
  facet_grid(VideoType~DATASET)

DT_wide%>%
    ggplot(aes(linearity_Original))+
  geom_histogram()


DT_wide%>%
    ggplot(aes(linearity_Morph))+
  geom_histogram()

```
