---
title: "Study2 Part 1 - Predicting emotion ratings"
author: '@H Cuve'
date: "16/07/2020"
output: html_document
---


load("D:/OneDrive - Nexus365/Face Morph Paper/Data/Study2_plots.RData"

# there is chaos and there there is my organisation method

```{r}
colnames(db_ASC_NT)
db_ASC_NT$Participant<- db_ASC_NT$ParticipantPrivateID

study2<- db_ASC_NT%>%
  subset(Group == "NT")%>%
  select(c(90,24,3:10,15,33,37, stim_id, Actor_ID))
saveRDS(study2, "study2.rds")
write_csv(study2, "study2.csv")
```

"remove some unnecessary duplicates


```{r eval=FALSE, include=FALSE}
rm(a_valence, a_valence1, acc_from_stimdiff, w,x,z,timebin_ADFES_avg_Anger, timebin_avg_Anger, timebin_avg_Disgust, timebin_avg_Fear, timebin_avg_Joy, timebin_avg_Sadness, timebin_avg_Surprise, timebin_JEFFE_avg_Anger, timebinout_avg_JEFFE, timebinout_avg_ADFES, timebin_shuff_Surprise, timebin_shuff_Sadness, timebin_shuff_JEFFE_Surprise, timebin_shuff_JEFFE_Joy, timebin_JEFFE_avg_Fear)

rm(timebin_random, timebin_random_ADFES, timebin_JEFFE_avg_Disgust, timebin_JEFFE_avg_Joy, timebin_JEFFE_avg_Surprise)
rm(timebin_JEFFE_avg_Sadness, timebin_random_JEFFE, timebin_shuff,timebin_shuff_Anger)

rm(timebin_shuff_ADFES, timebin_shuff_ADFES_Anger, timebin_shuff_Disgust, timebin_shuff_Fear, timebin_shuff_JEFFE, timebin_shuff_JEFFE_Anger, timebin_shuff_JEFFE_Anger)

rm(timebin_shuff_JEFFE_Disgust, timebin_shuff_JEFFE_Fear, timebin_shuff_JEFFE_Sadness, timebin_shuff_Joy)

rm(timestamp_ADFES, timestamp_ADFES_Anger, timestamp_ADFES_avg_Disgust, timestamp_ADFES_avg_Fear)

rm(whatsthisna, y, v1.1, v1, v1.2, testtemp, testpoly, test.data, test.data_avgface, test.data_avgface_96, test.data_avgface_ADFES, test.data_by_ADFES_avg_Anger)
rm(test.data1, test.data_by_ADFES_avg_Disgust, test.data_by_ADFES_avg_Fear, test.data_by_ADFES_avg_Surprise, testresults_ADFES_Fear, test.data_bySadness, test.data_byJEFFESurprise, test.data_byJEFFEJoy)
rm(test.data_avgface_jeffe)
rm(test_dcast, sum_cluster_sim, sum_cluster_sim_ADFES, sum_cluster_sim_final, sum_cluster_sim_JEFFE, sum_cluster_sim1)

rm(simularions, simulattion_vs_data, simulated_clusters_ADFES)
rm(simulattion_vs_data_ADFES, simulattion_vs_data_ADFES, simulattion_vs_data_JEFFE_test)
rm(simulattion_vs_data_JEFFE)

rm(simulated_clusters_current, simulated_clusters, simulated_clusters_ADFES_Anger, simulated_clusters_current, simulated_clusterstest_2, simulations)


rm(simulated_clusters_Anger, simulated_clusters_Disgust, simulated_clusters_Fear, simulated_clusters_JEFFE, simulated_clusterstest, simulated_clusters_JEFFE_Sadness)
rm(lmer_bin_random, lmer_bin_random_ADFES, lmer_bin_random_ADFES_Anger, lmer_bin_random_Disgust, lmer_bin_random_Disgust, lmer_bin_random_JEFFE_Anger, lmer_bin_random_summary)


rm(db_aus, db_of, db_of1, db_of4, db_of5, db_of5_new)

rm(db_of2, db_of5_coorrelations, db_of6, db_of6_new)

rm(db_of7_new_paper)
rm(db_of7_new_tomerge,db_of7_new_tomerge1, fuckup)

rm(timestamp_ADFES_avg_Anger, timestamp_ADFES_avg_Joy, timestamp_ADFES_avg_Sadness, timestamp_ADFES_avg_Surprise, timestamp_ADFES_Disgust, timestamp_ADFES_Fear, timestamp_ADFES_avg_Surprise, timestamp_ADFES_Surprise, timestamp_JEFFE_Surprise)

rm(timebinout, timebinout_avg, timestamp_ADFES_Joy, timestamp_JEFFE_Sadness, timestamp_avg_Disgust, timestamp_avg_Joy, timestamp_avg_Sadness, timestamp_JEFFE_Anger, timestamp_JEFFE_avg_Surprise)
rm(simulated_clusters_JEFFE_Anger, simulated_clusters_JEFFE_Disgust, simulated_clusters_JEFFE_Joy, simulated_clusters_JEFFE_Surprise, summarytest, summarytest_avg, summarytest_avg_ADFES, summarytest_avg_JEFFE)
rm(simulated_clusters_JEFFE_Fear, simulated_clusters_Joy, simulated_clusters_Sadness, simulated_clusters_Surprise)
rm(test.data_by_ADFES_avg_Joy, test.data_by_ADFES_avg_Sadness, test.data_by_avg_Anger, test.data_by_avg_Disgust, test.data_by_avg_Fear, test.data_by_avg_Fear, test.data_by_avg_Joy, test.data_by_avg_Sadness, test.data_by_avg_Surprise, testresults_avg_cluster_random, test.data_byADFESFear)
rm(testresults, testresults_ADFES, testresults_ADFES_Anger, testresults_ADFES_avg_Disgust, testresults_ADFES_avg_Joy)
```

Run proposed analyses

GLMMS

necessary packages
```{r}
library(afex)
library(lmerTest)
library(broom.mixed)
library(tidyverse)
library(emmeans)
library(sjmisc)
library(sjPlot) 
library(sjstats)
library(psycho)

```

# Predicting emotion ratings

lmer model on valence
```{r}
unique(db_ASC_NT$Video)
unique(substr(db_ASC_NT$Video, 1,3))

db_ASC_NT$Actor_ID<- as.factor(substr(db_ASC_NT$Video, 1,3))
unique(db_ASC_NT$Actor_ID)
str(db_ASC_NT)


db_ASC_NT$ParticipantPrivateID<- as.factor(db_ASC_NT$ParticipantPrivateID)
db_ASC_NT$Emotion<- as.factor(db_ASC_NT$Emotion)
db_ASC_NT$DATASET<- as.factor(db_ASC_NT$DATASET)
db_ASC_NT$VideoType<- as.factor(db_ASC_NT$VideoType)

# paper_analyses<- list()

paper_analyses$lmer_NT_val<- lmer(AnswerRating_Valence ~ 1 + VideoType + DATASET + Emotion+
                                    VideoType*Emotion*DATASET+(1| ParticipantPrivateID) + (1 | Video),
                                  REML = FALSE,
                                    data = subset(db_ASC_NT, db_ASC_NT$Group == "NT"))

paper_analyses$lmer_NT_val_analyze <- analyze (paper_analyses$lmer_NT_val, CI = 95, effsize_rules = "cohen1988")

# plot(paper_analyses$lmer_NT_val)
# qqnorm(resid(paper_analyses$lmer_NT_val))
# qqline(resid(paper_analyses$lmer_NT_val))

tab_model(paper_analyses$lmer_NT_val)

paper_analyses$lmer_NT_val_novt<- lmer(AnswerRating_Valence ~ 1 + DATASET + Emotion+
                                    Emotion*DATASET+(1| ParticipantPrivateID) + (1 | Video),
                                  REML = FALSE,
                                    data = subset(db_ASC_NT, db_ASC_NT$Group == "NT"))

paper_analyses$lmer_NT_val1 <- lmer(AnswerRating_Valence ~ 1 + DATASET + Emotion+
                                    VideoType*Emotion+
                                    DATASET*Emotion+
                                    # VideoType*Emotion*DATASET+ dropped insigifiant terms
                                    (1 | ParticipantPrivateID) + (1 | Video),
                                  REML = FALSE,
                                    data = subset(db_ASC_NT, db_ASC_NT$Group == "NT"))



```

# control for Actor ID instead
```{r}

paper_analyses$lmer_NT_val1_actID<- lmer(AnswerRating_Valence ~ 1 + DATASET + Emotion+
                                    VideoType*DATASET*Emotion+
                                    # DATASET*Emotion+
                                    # VideoType*Emotion*DATASET+ dropped insigifiant terms
                                    (1 | ParticipantPrivateID) + (1 | Actor_ID),
                                  REML = FALSE,
                                    data = subset(db_ASC_NT, db_ASC_NT$Group == "NT"))

anova(paper_analyses$lmer_NT_val1_actID, paper_analyses$lmer_NT_val1)
summary(paper_analyses$lmer_NT_val)
anova(paper_analyses$lmer_NT_val)
step(paper_analyses$lmer_NT_val)

std_beta(paper_analyses$lmer_NT_val)

# check if logarithmic transformation improves residuals
paper_analyses$lmer_NT_val1_log<- lmer(log1p(AnswerRating_Valence+.1) ~ 1 + DATASET + Emotion+
                                    VideoType*Emotion+
                                    DATASET*Emotion+
                                    # VideoType*Emotion*DATASET+ dropped insigifiant terms
                                    (1 | ParticipantPrivateID) + (1 | Video),
                                  REML = FALSE,
                                    data = subset(db_ASC_NT, db_ASC_NT$Group == "NT")) 

# the variance explained by actor ID is way less
# it doesn't
library(sjPlot)
library(sjmisc)
# sjmisc::
?plot_model
sjPlot::plot_model(paper_analyses$lmer_NT_val1, type = 'std')

summary(paper_analyses$lmer_NT_val)
anova(paper_analyses$lmer_NT_val)

plot(paper_analyses$lmer_NT_val1_log)
qqnorm(resid(paper_analyses$lmer_NT_val1_log))
qqline(resid(paper_analyses$lmer_NT_val1_log))

# 
plot(paper_analyses$lmer_NT_val1)
qqnorm(resid(paper_analyses$lmer_NT_val1))
qqline(resid(paper_analyses$lmer_NT_val1))


summary(paper_analyses$lmer_NT_val1)
anova(paper_analyses$lmer_NT_val1)

emmeans(paper_analyses$lmer_NT_val1, pairwise ~ VideoType*Emotion, adjust = "none")

# Only happiness turns out significant, so the anova seems a bit anti conservative?
# EMotion main contrasts
emmeans(paper_analyses$lmer_NT_val1, pairwise ~ Emotion, adjust = "bonf")
# all pairs differ except anger disgust, fear sadness, and anger sadness

# DATASET
library(emmeans)
paper_analyses$lmer_NT_val_DS<- emmeans(paper_analyses$lmer_NT_val, pairwise~ DATASET, adjust = "none")
# <- eff_size(emmeans(paper_analyses$lmer_NT_val, pairwise ~ DATASET, adjust = "none"))
paper_analyses$lmer_NT_val_DS


paper_analyses$lmer_NT_val_em<- emmeans(paper_analyses$lmer_NT_val, pairwise ~ Emotion, adjust = "none")


paper_analyses$lmer_NT_val_em<- emmeans(paper_analyses$lmer_NT_val, pairwise~ VideoType*Emotion, adjust = "none")


summary(paper_analyses$lmer_NT_val_em)
eff_size(paper_analyses$lmer_NT_val_DS, edf = paper_analyses$lmer_NT_val@vcov_varpar)
# consistent with anova


paper_analyses$lmer_NT_val$analyze_report<- analyze(paper_analyses$lmer_NT_val)
library(sjstats)
std_beta(paper_analyses$lmer_NT_val, ci.lvl = 0.95)

library(MuMIn)
r.squaredGLMM(paper_analyses$lmer_NT_val)
r.squaredGLMM(paper_analyses$lmer_NT_val_novt) #videotype makes a very small contribution
```


```{r}
dplyr::write_rds(db_ASC_NT, "db_ASC_NT.rds")
```


LMER intensity on full data


```{r}
db_ASC_NT$VideoType<- as.factor(db_ASC_NT$VideoType)
paper_analyses$lmer_NT_int2<- lmer(AnswerRating_Intensity ~ 
                                    VideoType + DATASET + Emotion+
                                    # VideoType+Emotion+
                                    # VideoType*Emotion*DATASET+ 
                                    (1 | ParticipantPrivateID) + (1 | Video),
                                  REML = FALSE,
                                    data = subset(db_ASC_NT, db_ASC_NT$Group == "NT" & db_ASC_NT$outlier_intensity == FALSE))

anova(paper_analyses$lmer_NT_int2)
summary(paper_analyses$lmer_NT_int2)
step(paper_analyses$lmer_NT_int2)

paper_analyses$lmer_NT_int1<- lmer(AnswerRating_Intensity ~ 
                                     DATASET + Emotion+
                                    # VideoType+Emotion+
                                    # VideoType*Emotion*DATASET+ 
                                    (1 | ParticipantPrivateID) + (1 | Video),
                                  REML = FALSE,
                                    data = subset(db_ASC_NT, db_ASC_NT$Group == "NT"))


emmeans(paper_analyses$lmer_NT_int, ~VideoType)
emm_options(lmerTest.limit = 10176)
emmeans(paper_analyses$lmer_NT_int, ~DATASET )

summary(paper_analyses$lmer_NT_int)
drop1(paper_analyses$lmer_NT_int)
anova(paper_analyses$lmer_NT_int)
step(paper_analyses$lmer_NT_int)

# we find only models of main effects no interactions on intensity
# Model found:
# AnswerRating_Intensity ~ VideoType + DATASET + Emotion + (1 | 
#     ParticipantPrivateID) + (1 | Video) + DATASET:Emotion


plot(paper_analyses$lmer_NT_int)
qqnorm(resid(paper_analyses$lmer_NT_int))
qqline(resid(paper_analyses$lmer_NT_int)) # broadly fine
r.squaredGLMM(paper_analyses$lmer_NT_int)
r.squaredGLMM(paper_analyses$lmer_NT_int1) #  small



paper_analyses$lmer_NT_int_analyze<- analyze(paper_analyses$lmer_NT_int,CI = 95, effsize_rules = "cohen1988")
paper_analyses$lmer_NT_int_analyze



```

lmer NATURALITY FUll

```{r}

db_ASC_NT$VideoType<- as.factor(db_ASC_NT$VideoType)
paper_analyses$lmer_NT_nat<- lmer(AnswerRating_Naturality ~ 
                                    VideoType + DATASET + Emotion+
                                    VideoType*Emotion+
                                    VideoType*DATASET+
                                    DATASET*Emotion+
                                    # VideoType*Emotion*DATASET+
                                    (1 | ParticipantPrivateID) + (1 | Video),
                                  REML = FALSE,
                                    data = subset(db_ASC_NT, db_ASC_NT$Group == "NT"))

anova(paper_analyses$lmer_NT_nat)
summary(paper_analyses$lmer_NT_nat)


paper_analyses$lmer_NT_nat1<- lmer(AnswerRating_Naturality ~ 
                                     DATASET + Emotion+
                                  
                                    DATASET*Emotion+
                                    # VideoType*Emotion*DATASET+
                                    (1 | ParticipantPrivateID) + (1 | Video),
                                  REML = FALSE,
                                    data = subset(db_ASC_NT, db_ASC_NT$Group == "NT"))


summary(paper_analyses$lmer_NT_nat)
emmeans(paper_analyses$lmer_NT_nat, pairwise~VideoType, adjust = "none")
drop1(paper_analyses$lmer_NT_nat)
anova(paper_analyses$lmer_NT_nat)
step(paper_analyses$lmer_NT_nat) 


paper_analyses$lmer_NT_nat_analyze<- analyze(paper_analyses$lmer_NT_nat, CI = 95)

# consistent with anova, all main effects significant apart from Video Type and all interaction significant apart from three-way
paper_analyses$lmer_NT_nat_VT_DS <- emmeans(paper_analyses$lmer_NT_nat,pairwise~ VideoType*DATASET)
paper_analyses$lmer_NT_nat_VT_DS
# test the specific effects
# consistent with anovas, morphs are more natural for ADFES and less natural for JEFFE

# VideoType*EMotion
paper_analyses$lmer_NT_nat_VT_EM <- emmeans(paper_analyses$lmer_NT_nat,pairwise~ VideoType*Emotion, adjust = "none")
paper_analyses$lmer_NT_nat_VT_EM
# again emotion effects seem to be driven by happiness



# model found
# AnswerRating_Naturality ~ VideoType + DATASET + Emotion + (1 | 
#     ParticipantPrivateID) + (1 | Video) + VideoType:Emotion + 
#     VideoType:DATASET + DATASET:Emotion


plot(paper_analyses$lmer_NT_nat)
paper_analyses$lmer_NT_nat_DS_EM <- emmeans(paper_analyses$lmer_NT_nat,pairwise~ DATASET*Emotion, adjust = "none")
paper_analyses$lmer_NT_nat_DS_EM

EMqqnorm(resid(paper_analyses$lmer_NT_nat))
qqline(resid(paper_analyses$lmer_NT_nat)) fine

r.squaredGLMM(paper_analyses$lmer_NT_nat)
r.squaredGLMM(paper_analyses$lmer_NT_nat1)

```


Accuracy

```{r}
min(db_NT_anova$Recognacc)
max(db_NT_anova$Recognacc)
unique(db_NT_anova$Recognacc)
db_NT_anova$Recognacc

min(db_NT_anova$Recognacc_log)
max(db_NT_anova$Recognacc_log)
```


Full glmer on ACCURACY


```{r}
db_ASC_NT$VideoType<- as.factor(db_ASC_NT$VideoType)
unique(db_ASC_NT$Recognacc)
paper_analyses$glmer_NT_acc<- glmer(Recognacc ~ 
                                    VideoType + DATASET + Emotion+
                                    VideoType*Emotion+
                                    VideoType*DATASET+
                                    # DATASET*Emotion+
                                    # VideoType*Emotion*DATASET+
                                    (1 | ParticipantPrivateID) + (1 | Video),
                                  # REML = FALSE,
                                  family = 'binomial',
                                    data = subset(db_ASC_NT, db_ASC_NT$Group == "NT"),
                                  )
library(ggeffects)
# Note the use of the "all"-tag here, see help for details
ggpredict(paper_analyses$glmer_NT_acc, "VideoType") %>% plot()

emmeans::emmeans(paper_analyses$glmer_NT_acc, ~ VideoType, type = "response")
emmeans::emmeans(paper_analyses$glmer_NT_acc, ~DATASET* VideoType, type = "response")

```


```{r}
paper_analyses$glmer_NT_acc_noem<- glmer(Recognacc ~ 
                                    VideoType + DATASET+
                                    # VideoType* Emotion+
                                    VideoType*DATASET+
                                    # DATASET*Emotion+
                                    # VideoType*Emotion*DATASET+
                                    (1 | ParticipantPrivateID) + (1 | Video),
                                  # REML = FALSE,
                                  family = 'binomial',
                                    data = subset(db_ASC_NT, db_ASC_NT$Group == "NT"),
                                  )


paper_analyses$glmer_NT_acc1<- glmer(Recognacc ~ 
                                    VideoType + DATASET + Emotion+
                                    VideoType*Emotion+
                                    VideoType*DATASET+
                                    # DATASET*Emotion+
                                    # VideoType*Emotion*DATASET+
                                    (1 | ParticipantPrivateID) + (1 | Video),
                                  # REML = FALSE,
                                  family = 'binomial',
                                    data = subset(db_NT_lmer, db_NT_lmer$ReactionTime_Recognition_outlier == "YES"),
                                  )


summary(paper_analyses$glmer_NT_acc1)
anova(paper_analyses$glmer_NT_acc1)
anova(paper_analyses$glmer_NT_acc)
anova(paper_analyses$glmer_NT_acc,paper_analyses$glmer_NT_acc_noem)

acc_emm<- emmeans(paper_analyses$glmer_NT_acc1, pairwise~VideoType, adjust = "none")
?eff_size

emmeans(paper_analyses$glmer_NT_acc1, pairwise~DATASET, adjust = "none")
emmeans(paper_analyses$glmer_NT_acc1, pairwise~VideoType*DATASET, adjust = "none")

emmeans(paper_analyses$glmer_NT_acc1, pairwise~VideoType*DATASET, adjust = "none")

emmeans(paper_analyses$glmer_NT_acc1, pairwise~VideoType*Emotion, adjust = "none")

emmeans(paper_analyses$glmer_NT_acc1, pairwise~Emotion, adjust = "holm")

# <!-- p.adjust(0.0040, n = 2) -->

# eff_size(pairs(acc_emm),sigma(paper_analyses$glmer_NT_acc@dev),  edf = 105 )


```


```{r}
summary(paper_analyses$glmer_NT_acc)

relgrad <- with(paper_analyses$glmer_NT_acc@optinfo$derivs,solve(Hessian,gradient))
max(abs(relgrad))
drop1(paper_analyses$glmer_NT_acc)
anova(paper_analyses$glmer_NT_acc)
step(paper_analyses$glmer_NT_acc)

# consistent with anova for the most part except no ME of videotype, all main effects significant apart from Video no interaction with video type either
paper_analyses$glmer_NT_acc_VT_DS <- emmeans(paper_analyses$glmer_NT_acc,pairwise~ VideoType*DATASET, adjust = "none")
paper_analyses$glmer_NT_acc_VT_DS # accuracy different in JEFFE

# test the specific effects
# consistent with anovas, morphs are more natural for ADFES and less natural for JEFFE

# VideoType*EMotion
paper_analyses$glmer_NT_acc_VT_EM <- emmeans(paper_analyses$glmer_NT_acc,pairwise~ VideoType*Emotion, adjust = "none")
paper_analyses$glmer_NT_acc_VT_EM
# No pairwise reaches significance


plot(paper_analyses$glmer_NT_acc)
qqnorm(resid(paper_analyses$glmer_NT_acc))
qqline(resid(paper_analyses$glmer_NT_acc))


r.squaredGLMM(paper_analyses$glmer_NT_acc)
r.squaredGLMM(paper_analyses$glmer_NT_acc1)
anova(paper_analyses$glmer_NT_acc, paper_analyses$glmer_NT_acc1)
paper_analyses$glmer_NT_acc_analyze<- analyze(paper_analyses$glmer_NT_acc)
paper_analyses$glmer_NT_acc


```


To do
- similarity and confusion analyses scripts